---
title: "Sample characteristics"
date: "Last updated `r Sys.Date()`"
output: 
  html_document:
    toc: FALSE
    code_folding: hide
---

<u>To cite these data:</u>

[add data paper reference here]

This page shows the demographic characteristics for the sample of participants who responded to the items. The sample contained participants from a wide range of ages, household incomes, and different geographies (by state) within the US. Slightly more than half of the sample identified as female, 73% reported identifying as White, and the majority had some college-level education (42%) or a high school degree/GED equivalent (40%). 

Note that most of the participants in the sample entered the survey through Prolific (90.7%); the remainder entered through Amazon's Mechanical Turk platform. Participants were allowed to complete the survey multiple times, as each version of the survey contained only a small (random) subset of all possible terms. In other words, the possiblity of responding to the same term twice was low. The final figure on this page demonstrates that the majority of participants completed the survey only once (44%) or twice (35%). Participants were compensated at the US minimum wage rate (at the time of data collection) using the mean response time as an estimate of the time required.

The data can be downloaded [here](https://doi.org/10.7910/DVN/5T80PF).

Please consult the reference listed above for more information about this project.

```{r, include = F}
knitr::opts_chunk$set(message = F, warning = F)
```

```{r}
library(tidyverse)
library(here)
library(ggpubr)
library(knitr)
library(kableExtra)
library(maps)

data = read.csv(here("data/TDA_data_scored.csv"))

data = filter(data, included == "Yes")
```


```{r}
data = data %>%
  group_by(PID) %>%
  mutate(n = n()) 

data_part = data %>%
  group_by(PID) %>%
  filter(row_number() == 1) %>%
  ungroup()
```

## Age

```{r}
# Here we show code for analyzing the data by response instead of participant
# data %>%
#   ggplot(aes(x = age)) +
#   geom_histogram(binwidth = 1, color = "white") +
#   labs(title = "Age in years", x= NULL) +
#   theme_pubr()
```


```{r}
data_part %>%
  ggplot(aes(x = age)) +
  geom_histogram(binwidth = 1, color = "white") +
  labs(title = "Age in years", x= NULL) +
  theme_pubr()
```

## Sex{.tabset}

```{r}
# Here we show code for analyzing the data by response instead of participant
# data %>%
#   group_by(sex) %>%
#   count() %>%
#   ungroup() %>%
#   mutate(percent = 100*(n/sum(n)),
#          percent = round(percent),
#          percent = paste(percent, "%")) %>%
#   ggplot(aes(x = sex, y = n)) +
#   geom_bar(stat = "identity") +
#   geom_text(aes(label = percent), vjust = 0) +
#   labs(title = "What was your biological sex at birth", x= NULL) +
#   theme_pubr()
```

```{r}
data_part %>%
 group_by(sex) %>%
  count() %>%
  ungroup() %>%
  mutate(percent = 100*(n/sum(n)),
         percent = round(percent),
         percent = paste(percent, "%")) %>%
  ggplot(aes(x = sex, y = n)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = percent), vjust = 0) +
  labs(title = "What was your biological sex at birth", x= NULL) +
  theme_pubr()
```

## Education{.tabset}

```{r}
# Here we show code for analyzing the data by response instead of participant
# data %>%
#   mutate(edu = factor(edu, levels = c(
#       "Less than 12 years", 
#       "High school grad/GED",
#       "Currently in college/university",
#       "Some college/university, but did not graduate",
#       "Associate degree (2 yr)",
#       "College/university degree (4 yr)",
#       "Currently in grad/professional school",
#       "Grad/professional degree"
#   ))) %>%
#   group_by(edu) %>%
#   count() %>%
#   ungroup() %>%
#   mutate(percent = 100*(n/sum(n)),
#          percent = round(percent),
#          percent = paste(percent, "%")) %>%
#   ggplot(aes(x = edu, y = n)) +
#   geom_bar(stat = "identity") +
#   geom_text(aes(label = percent), vjust = 0) +
#   labs(title = "Level of education", x= NULL) +
#   theme_pubr() +
#   theme(axis.text.x = element_text(angle = 65, vjust =1, hjust = 1))
```


```{r}
data_part %>%
  mutate(edu = factor(edu, levels = c(
      "Less than 12 years", 
      "High school grad/GED",
      "Currently in college/university",
      "Some college/university, but did not graduate",
      "Associate degree (2 yr)",
      "College/university degree (4 yr)",
      "Currently in grad/professional school",
      "Grad/professional degree"
  ))) %>%
  group_by(edu) %>%
  count() %>%
  ungroup() %>%
  mutate(percent = 100*(n/sum(n)),
         percent = round(percent),
         percent = paste(percent, "%")) %>%
  ggplot(aes(x = edu, y = n)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = percent), vjust = 0) +
  labs(title = "Level of education", x= NULL) +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 65, vjust =1, hjust = 1))
```

## Ethnicity{.tabset}

```{r}
# Here we show code for analyzing the data by response instead of participant
# data %>%
#   mutate(ethnic = factor(ethnic, levels = c(
#      "American Indian/Alaskan Native",
#      "Asian",
#      "Black",
#      "Hispanic",
#      "White",
#      "Mixed (two or more)",
#      "Other"
#   ))) %>%
#   group_by(ethnic) %>%
#   count() %>%
#   ungroup() %>%
#   mutate(percent = 100*(n/sum(n)),
#          percent = round(percent),
#          percent = paste(percent, "%")) %>%
#   ggplot(aes(x = ethnic, y = n)) +
#   geom_bar(stat = "identity") +
#   geom_text(aes(label = percent), vjust = 0) +
#   labs(title = "Racial/ethnic identity", x= NULL) +
#   theme_pubr() +
#   theme(axis.text.x = element_text(angle = 65, vjust =1, hjust = 1))
```

```{r}
data_part %>%
  mutate(ethnic = factor(ethnic, levels = c(
     "American Indian/Alaskan Native",
     "Asian",
     "Black",
     "Hispanic",
     "White",
     "Mixed (two or more)",
     "Other"
  ))) %>%
  group_by(ethnic) %>%
  count() %>%
  ungroup() %>%
  mutate(percent = 100*(n/sum(n)),
         percent = round(percent),
         percent = paste(percent, "%")) %>%
  ggplot(aes(x = ethnic, y = n)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = percent), vjust = 0) +
  labs(title = "Racial/ethnic identity", x= NULL) +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 65, vjust =1, hjust = 1))
```

## Household income{.tabset}

```{r}
# Here we show code for analyzing the data by response instead of participant
# data %>%
#   mutate(hhinc = factor(hhinc, levels = c(
#       "< 20K",
#       "20K-40K",
#       "40K-60K",
#       "60K-80K",
#       "80K-100K",
#       "100K-120K",
#       "120K-150K",
#       "150K-200K",
#       "200K-250K",
#        "250K-350K",
#        "350K-500K",
#        "> 500K"
#   ))) %>%
#   group_by(hhinc) %>%
#   count() %>%
#   ungroup() %>%
#   mutate(percent = 100*(n/sum(n)),
#          percent = round(percent),
#          percent = paste(percent, "%")) %>%
#   ggplot(aes(x = hhinc, y = n)) +
#   geom_bar(stat = "identity") +
#   geom_text(aes(label = percent), vjust = 0) +
#   labs(title = "Household Income", x= NULL) +
#   theme_pubr() +
#   theme(axis.text.x = element_text(angle = 65, vjust =1, hjust = 1))
```


```{r}
data_part %>%
  mutate(hhinc = factor(hhinc, levels = c(
      "< 20K",
      "20K-40K",
      "40K-60K",
      "60K-80K",
      "80K-100K",
      "100K-120K",
      "120K-150K",
      "150K-200K",
      "200K-250K",
       "250K-350K",
       "350K-500K",
       "> 500K"
  ))) %>%
  group_by(hhinc) %>%
  count() %>%
  ungroup() %>%
  mutate(percent = 100*(n/sum(n)),
         percent = round(percent),
         percent = paste(percent, "%")) %>%
  ggplot(aes(x = hhinc, y = n)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = percent), vjust = 0) +
  labs(title = "Household Income", x= NULL) +
  theme_pubr() +
  theme(axis.text.x = element_text(angle = 65, vjust =1, hjust = 1))
```

# State of residence{.tabset}

## Thing

```{r, fig.height=10}
data_part %>% 
  filter(!is.na(state)) %>% 
  group_by(state) %>% 
  count() %>% 
  ggplot(aes(x = reorder(state, n), y = n)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(x = NULL, y = "Count") +
  theme_pubr() 
```


## Map

```{r}
MainStates <- map_data("state")

data_part %>% 
  with_groups(state, count) %>% 
  mutate(region = tolower(state)) %>% 
  inner_join(MainStates) %>% 
  ggplot() + 
  geom_polygon(aes(x=long, y=lat, group=group, fill = n),
                color="black") +
  scale_x_continuous(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  labs(x = NULL, y = NULL) +
  theme_pubr()
```


# Participant response rates

```{r}
data %>%
  group_by(PID) %>%
  count() %>%
  ggplot(aes(x = n)) +
  geom_bar(stat = "count") +
  scale_x_continuous(breaks = 1:13) +
  labs(title = "Number of times participated in survey",
       x = NULL) +
  theme_pubr()
```


