---
title: "TDA Difficulty"
date: "Last updated `r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    code_folding: hide
---

To cite these data:
[add data paper reference here]

We present here the *average* difficulty of 2,818 trait descriptive adjectives (TDAs) in American English. The average difficulty for each TDA was derived from the survey administration of two different, randomly-generated "definition-term" vocabulary items. 

On this page, we report the total number of responses across both forms of the item, as well as the average proportion correct across both forms. Two forms were used to reduce variability in the proportion correct resulting from the random generation of alternative response choices (i.e., distractors).

The total proportion correct provides an indication of both familiarity of the adjective and consensus among raters about its meaning, especially as a descriptor of personality. For example, most of the terms with a low proportion of correct responses are unfamiliar to many individuals (i.e., rarely encountered in everyday language) -- "goatish" (.07), "pithy" (.10), "splenetic" (.10). Other terms -- "dizzying" (.04), "smooth" (.09) -- are familiar but ambiguous in meaning relative to personality. By contrast, terms with the highest proportion of correct responses are familiar and unambiguous -- "jolly" (1.00), "thankful" (1.00), "unreliable" (.99).

Statistics from the individual administrations of each term can be found [here](https://pie-lab.github.io/tda/item-difficulty.html).

The data can be downloaded [here](XXXXX)

Please consult the reference listed above for more information about this project.

```{r, include = F}
knitr::opts_chunk$set(echo = T, message = F, warning = F)
```

```{r}
library(here) # for engaging with working environment
library(tidyverse) # for data cleaning and manipulation
library(Hmisc) # for weighted means
library(DT) # for viewing data tables

data = read_csv(here("data/TDA_data_scored.csv"))
masterKey = read_csv(here("data/masterkey.csv"))

data = data %>%
  filter(included == "Yes") %>% # remove participants screend out for demographic and quality reasons
  select(starts_with("q_")) # select only TDA items

data_means = colMeans(data, na.rm = T) #calculate column means

all_item_means = data.frame( # create data frame with...
  item = names(data_means), # ...variable name and...
  prop_correct = data_means #... proportion correct
)

item_prop = masterKey %>% # join the masterKey (item name, correct adjective, and form)
  full_join(all_item_means) %>% # with proportion correct
  mutate(prop_correct = round(prop_correct, 2)) # round to 2 decimal places

# next we count the number of administrations of each item
item_prop$N = colSums(!is.na(data)) # count non-missing

```

```{r}
# create table 
item_prop = item_prop %>%
  group_by(adjective) %>% # for each unique adjective
  mutate(weight = N/sum(N)) %>% # create a new variable that is the number of responses (per item) divided by the total number of responses (across both items)
  summarise(
    N = sum(N), # how many total responses 
    prop = wtd.mean(prop_correct, weights = weight, na.rm=T) # average proportion, weighted by sample size
  ) %>%
  mutate(prop = round(prop, 2)) # round to 2

item_prop %>%
  DT::datatable( # put into interactive HTML table
    colnames = c("Adjective", "N (total)", "Proportion Correct"), #colnames
    filter = "top", # can filter
    rownames = F # don't need rownames
  )
```

```{r}
write_csv(item_prop, file = here("data/tda_difficulty.csv"))
```



